Preparing a manuscript for a peer-reviewed journal the FMDL way

### 2023-02-22 ReviewerResponseWXYZ-N.tex

% N is the number of the review cycle you are in. If this is the first review report that we are responding to, N=1.

% So, for a review response to Advanced Functional Materials, where this is our second response to the reviewers, the name of the file should be ReviewerResponseADFM-2.tex

% We could have chosen to keep things simple and rely on GitHub to store old versions. The problem with that idea is that sometimes you need to cite/attach earlier responses in communications with journals, and it is more sensible to have an unmodified document on hand.

\documentclass[12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Required packages
\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{physics}
\doublespacing
\usepackage{subfigure}
\usepackage{float}
%\usepackage{caption}
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{romannum}
\usepackage{caption} % For Table of Contents entry
\usepackage{xr} % For referencing portions of external documents, such as your main manuscript.
\usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
\addbibresource{publishing.bib} % Replace this with the name of your .bib file.
\usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
\DeclareSIUnit{\Molar}{M}
\DeclareSIPrefix\micro{\text{\textmu}}{-3}
\DeclareSIUnit\angstrom{\text {Å}}
\DeclareSIUnit\gauss{G}

\externaldocument[main:]{IITD_Manuscript} % Replace this with the name of the file you are using for your main manuscript - you will be referencing locations in that file, by prefixing all references there with "main:". Citations can be handled the same way. You may have to "clean" all temporary files to make this work. See usage example below.

@@

\date{}
\begin{document}

\maketitle

We would like to thank the editor for arranging a careful review of this manuscript. We have gone through the reviewer comments in detail, and as requested, have carried out estimates of the obtained quantities after including corrections pointed out by the reviewers. We are thankful to the reviewers for their incisive and helpful comments.

Below, we list the changes made in response to reviewer comments and requests. The changes made have been incorporated in the manuscript as per requirements. The related figures have also been updated in the manuscript, if needed. For your convenience, a marked copy of the manuscript also submitted with changes in text and equations marked (red=deletion, blue=addition).

@@

\textbf{Note to student}: No actual changes in the manuscript are supposed to be included below. Only their locations, and the reasoning/response are located in this document.

\textbf{Note to student}: No changes are marked up in the original document. The deletion (red) and addition (blue) markup is generated by my shell script that compares two checkpoints: a) last submission, b) pre-final draft and generates the difference tex file and pdf document automatically using git and latexdiff. Do not waste your time on marking up changes in the main document.

\begin{enumerate}
\item \textbf{Reviewer 1} % \textit{You can add as many items as needed below for this reviewer. Break up larger paragraphs into separate items which pertain to separate points. All text by the reviewer must be quoted in textit's, without \textbf{any} modifications. We are quoting the reviewer - it must be verbatim (not even a space bar or extra comma should be missing, even if there are grammatical or spellings errors).}
  \begin{enumerate}
  \item \textit{Comment 1 by reviewer 1.}

    Response: Your response goes here. As shown in previous work\cite{goossens:1994}, the quantity A is expected to increase when parameter B is reduced. Our results are consistent with that. However, the reviewer's criticism that a different starting concentration could have been used to improve the S/N ratio is very helpful. Accordingly, we have repeated our measurements (results are in Fig.~4(c) of the main manuscript). The resulting changes have been summarized in Table~(\ref{tbl:discrepancy}).

@@

  \item \textit{Comment 2 by reviewer 1.}

    Response: Your response goes here.

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page \pageref{main:page:rev1q2}, line \ref{main:line:rev1q2}: we have ...
    \item On page 5, column 1, line 20: we have ...
    \item Figure \ref{main:fig:revisedtem} has been updated with the new results.
    \item References \cite{main:virtanen:2020}, \cite{main:perez:2011} and \cite{main:stancin:2019} have been added to the manuscript.
    \end{itemize}
  \end{enumerate}

\item \textbf{Reviewer 2} % \textit{You can add as many items as needed below for this reviewer. Break up larger paragraphs into separate items which pertain to separate points. All text by the reviewer must be quoted in textit's, without \textbf{any} modifications. We are quoting the reviewer - it must be verbatim.}
  \begin{enumerate}
  \item \textit{Comment 1 by reviewer 2.}

    Response: Your response goes here.

@@

    Response: Your response goes here.

    Changes marked in the manuscript:

    \begin{itemize}
    \item On page 1, column 2, line 6: we have ...
    \item On page 5, column 1, line 20: we have ...
    \item Figure 2(b) has been updated with the new results.
    \item References [11] and [42] have been added to the manuscript.
    \end{itemize}
  \end{enumerate}

\item \textbf{Reviewer 3} % \textit{You can add as many items as needed below for this reviewer. Break up larger paragraphs into separate items which pertain to separate points. All text by the reviewer must be quoted in textit's, without \textbf{any} modifications. We are quoting the reviewer - it must be verbatim.}
  \begin{enumerate}
  \item \textit{Comment 1 by reviewer 3.}

    Response: Your response goes here.

### 2023-02-23 Rev_SolProc.tex
Initial commit. Blank manuscript

\documentclass[12 pt]{article}

@@

\begin{center}
  \begin{longtable}{p{3cm}p{5cm}p{3.5cm}p{2.5cm}}
    \caption{Naming things. Mandatory parts of the string in the name/label are in blue color. DOCNAME refers to the usage in the README file of this repo.} \label{tbl:namingthings}\\
    \hline
    \textbf{Entity}  & \textbf{Purpose of the entity} &  \textbf{Good usage} & \textbf{Examples of poor choices} \\\hline
    Label to an equation & To label an equation so that it can be used in a cross-reference & \textcolor{blue}{eqn:}energyofparticle & Eq12, importantequation \\\hline
    Label to a figure & To label a figure so that it can be used in a cross-reference & \textcolor{blue}{fig:}JVdata & Fig1 \\\hline
    Label to a table & To label a table so that it can be used in a cross-reference & \textcolor{blue}{tbl:}ratio & Table1, reallyimportantsummary \\\hline
    Label to a section & To label a section in the document so that it can be used in a cross-reference & \textcolor{blue}{sec:}discussion & Sec1 \\\hline
    Name of a figure file & To name a figure file that can be subsequently called in includegraphics markup & JVdata.eps & Fig1b.eps, firstfigure.eps\\\hline
    Name of the bibliography file & To name the .bib file that you will be using in this document & \textcolor{blue}{DOCNAME.bib} & references.bib \\\hline
  \end{longtable}
\end{center}

@@

\begin{figure}
\centering
\subfigure[Measured capacitance as a function of area.]{\label{fig:ca}\includegraphics[width=88mm,keepaspectratio]{example-image-a}}
\subfigure[C(f) for different biases.]{\label{fig:cfv}\includegraphics[width=88mm,keepaspectratio]{example-image-b}}
\caption{(a) Use clear images, preferably in .eps form for anything other than scan data, and (b) .png form for scan data. The width of the figure is chosen to be 88mm since that is the typical width of a journal column in two-column format. Your figures must be clear to read easily at this size. If your figure is too wide to fit in this width, you can use the figure* environment, but that is done only in very rare cases where the figure is really complex.}
\label{fig:cv}
\end{figure}

@@

\begin{table}
  \caption{An example table}
  \label{tbl:ratio}
  \begin{center}
    \begin{tabular}{cccccc}
      x  & Thickness & & \multicolumn{3}{c}{Composition: EDX and (XPS)} \\
         & (nm) & & K/A & Na/A & Nb/A \\
      \hline \\
      0.3 & 62 $\pm$ 4 & & 0.365 $\pm 2\%$ & 0.634 $\pm 2\%$ & 1.036 $\pm 2\%$ \\
         & & & (0.3375) & (0.6624) & (1.028) \\
      \hline \\
      0.5 & 70 $\pm$ 2 & & 0.510 $\pm 2\%$ & 0.489 $\pm 2\%$ & 0.937 $\pm 2\%$ \\
         & & & (0.5091) & (0.4910) & (1.037) \\
      \hline \\
      0.7 & 68 $\pm$ 2 & & 0.718 $\pm 2\%$ & 0.281 $\pm 2\%$ & 0.928 $\pm 2\%$ \\
         & & & (0.7682) & (0.2317) & (1.153) \\
      \hline \\
    \end{tabular}
  \end{center}
\end{table}

@@

>>>>

\documentclass[12pt,twocolumn]{article}

@@

\scriptsize
\begin{table}
  \centering
  \caption{Naming things. Mandatory parts of the string in the name/label are in blue color. DOCNAME refers to the usage in the README file of this repo.} \label{tbl:namingthings}
  \begin{tabular}{p{1.5cm}p{2.5cm}p{3cm}p{2cm}}
    \hline
    \textbf{Entity}  & \textbf{Purpose of the entity} &  \textbf{Good usage} & \textbf{Examples of poor choices} \\\hline
    Label to an equation & To label an equation so that it can be used in a cross-reference & \textcolor{blue}{eqn:}energyparticle & Eq12, importantequation \\\hline
    Label to a figure & To label a figure so that it can be used in a cross-reference & \textcolor{blue}{fig:}JVdata & Fig1 \\\hline
    Label to a table & To label a table so that it can be used in a cross-reference & \textcolor{blue}{tbl:}ratio & Table1, reallyimportantsummary \\\hline
    Label to a section & To label a section in the document so that it can be used in a cross-reference & \textcolor{blue}{sec:}discussion & Sec1 \\\hline
    Name of a figure file & To name a figure file that can be subsequently called in includegraphics markup & JVdata.eps & Fig1b.eps, firstfigure.eps\\\hline
    Name of the bibliography file & To name the .bib file that you will be using in this document & \textcolor{blue}{DOCNAME.bib} & references.bib \\\hline
  \end{tabular}
\end{table}
\normalsize

@@

\begin{figure}
  \centering
  \begin{subfigure}{80mm}
    \centering
    \includegraphics[width=\textwidth]{example-image-a}
    \caption{Measured capacitance as a function of area.}
    \label{fig:ca}
  \end{subfigure}
  \hfill
  \begin{subfigure}{80mm}
    \centering
    \includegraphics[width=\textwidth]{example-image-b}
    \caption{C(f) for different biases.}
    \label{fig:cfv}
  \end{subfigure}
  \caption{\subref{fig:ca} Use clear images, preferably in .eps form for anything other than scan data, and \subref{fig:cfv} .png form for scan data. The width of the figure is chosen to be 80mm since that is the typical width of a journal column in two-column format. Your figures must be clear to read easily at this size. If your figure is too wide to fit in this width, you can use the figure* environment, but that is done only in very rare cases where the figure is really complex. In case, we switch to using a large figure panel that cuts across two columns, each subfigure will need to be reduced to a width of around 40mm (for 2 in a row) or 27 cm (for 3 in a row), and so on.}
  \label{fig:cv}
\end{figure}

@@

\begin{table}
  \caption{An example table. The width of this table is controllable using p parameters instead of merely centering everything. For large tables, we may have to use both columns.}
  \label{tbl:ratio}
  \begin{center}
    \begin{tabular}{cccccc}
      x  & Thickness & & \multicolumn{3}{c}{Composition: EDX and (XPS)} \\
         & (nm) & & K/A & Na/A & Nb/A \\
      \hline \\
      0.3 & 62 $\pm$ 4 & & 0.365 $\pm 2\%$ & 0.634 $\pm 2\%$ & 1.036 $\pm 2\%$ \\
         & & & (0.3375) & (0.6624) & (1.028) \\
      \hline \\
      0.5 & 70 $\pm$ 2 & & 0.510 $\pm 2\%$ & 0.489 $\pm 2\%$ & 0.937 $\pm 2\%$ \\
         & & & (0.5091) & (0.4910) & (1.037) \\
      \hline \\
      0.7 & 68 $\pm$ 2 & & 0.718 $\pm 2\%$ & 0.281 $\pm 2\%$ & 0.928 $\pm 2\%$ \\
         & & & (0.7682) & (0.2317) & (1.153) \\
      \hline \\
    \end{tabular}
  \end{center}
\end{table}

@@

This part demonstrates how to add things here during revisions and how to correctly refer to them in the reviewer response document:

\begin{figure}
  \centering
  \begin{subfigure}{42mm}
    \centering
    \includegraphics[width=\textwidth]{example-image-a}
    \caption{High-resolution TEM data.}
    \label{fig:hrtem}
  \end{subfigure}
  \hfill
  \begin{subfigure}{42mm}
    \centering
    \includegraphics[width=\textwidth]{example-image-b}
    \caption{Percentage coverage (from SEM data).}
    \label{fig:surfacecoverage}
  \end{subfigure}
  \caption{\subref{fig:hrtem} This could be a response to revisions requested by a reviewer. \subref{fig:surfacecoverage}  You can use the labels used here in the response document since we have used package xr there, and defined this manuscript file as the external document there.}
  \label{fig:revisedtem}
\end{figure}

High-resolution TEM data and surface coverage extracted from SEM data (Fig.~(\ref{fig:revisedtem})) which was analyzed using SciPy\cite{virtanen:2020}, which is a Python\cite{perez:2011,stancin:2019} library used for such tasks. indicate that surface roughness cannot be a candidate explanation for the observed high leakage current in the device. Instead, charge storage in the disordered film may be released over time. This aspect will be studied in a forthcoming paper\label{page:rev1q2}\linelabel{line:rev1q2}.
